
	\renewcommand\thesection{\Alph{section}.}
	\section{Fines}
		This is a summary of all fines specified elsewhere in these Rules, Regulations, and Procedures. A fine may be levied against any organization for failure to complete a responsibility. If one or more organizations cover for said responsibility, the fine shall be awarded to them and split at the discretion of the Sweepstakes Chairman, or anyone designated by that Chairman. The list of responsibilities and fines includes:

		\begin{itemize}

			\item Barricaders at barricades with proper equipment: \$20 per barricader (sec. \ref{subsec:Barricaders})
			
			\item Sweepers with proper equipment: \$15, \$30 per sweeper (sec. \ref{subsec:Sweepers})
			
			\item Driver extraction equipment in the follow car: \$15, \$25 per occurrence (sec. \ref{subsec:Follow Cars}, sec. \ref{subsubsec:Follow Car})
			
			\item Chute flagger: \$10, \$25 per occurrence (sec. \ref{subsec:Flaggers})
			
			\item Stop at a yellow stop flag on the course: \$90 per occurrence, \$90 per occurence + Team DQ (sec. \ref{subsec:Flaggers}) %\ref*{subsubsec:Driving}

			\item Representation at a Sweepstakes Committee meeting: \$15 per meeting (sec. \ref{subsec:Meetings})

			\item Pass a spot safety check: \$25 for the first occurrence, \$50 thereafter (sec. \ref{subsec:Spot Safety})
			
			\item Lights and reflectors during darkness: \$20 per buggy per occurrence (sec. \ref{subsec:Freeroll Buggies})

			\item No-Parking signs: \$25, \$50 (sec. \ref{subsec:NoParking})
			
			\item Barricades: \$15 during push practice, otherwise \$25, \$50 per occurrence (sec. \ref{subsec:Freeroll Barricades}, sec. \ref{subsec:Barricades})

			\item Hay bales: \$25, \$50 per occurrence (sec. \ref{subsec:Haybales})
			
			\item Warning signs: \$25, \$50 per occurrence (sec. \ref{subsec:WarnSigns})

			\item Paint lane and zone markings: \$25 per occurrence (sec. \ref{subsec:Lanes})

			\item Course watch duty: \$25 per person or vehicle (sec. \ref{subsec:Course Watch})

			\item Crowd control barriers: \$50 per occurrence (sec. \ref{subsec:Crowd Control})

			\item Course marshals with proper equipment: \$25 per course marshal (sec. \ref{subsec:Course Marshals})
			
			\item Maintain safety in a buggy preparation area: \$50, \$100+Team DQ (sec. , sec. \ref{subsec:Buggy Prep})

		\end{itemize}

		\noindent Fine amounts are indicated in the following order where applicable: \newline
		freeroll/push practice, day of Sweepstakes racing

