\chapter{Entry Requirements and Procedures}

\section{Race Competition Classes}

	There shall be three classes of race competition. These classes shall be known as the men's races, women's races, and all gender races. 

	Additional information about these classes can be found in Appendix \ref*{All Gender}

\section{Race Entry Requirements}

\subsection{Entry}

An entry shall consist of one buggy, one team, and one alternate team. No pusher may compete on more than one entry on any single day of competition. No driver may compete on more than one entry in each class of race competition (one men's race and one women's race) on any single day of competition. No buggy may be used by more than one entry in each class of race competition (one men's race and one women's race) on any single day of competition. All alternate teams are also bound by these conditions. Each organization must submit to the Sweepstakes Chairman, or anyone designated by that Chairman, a list for each of its entries. The list must include the entry's buggy, all of the members of the entry's team, and all of the members of the entry's alternate team. All entry lists must be submitted by noon on the day before the preliminary races are scheduled to be held. In entering members, Sweepstakes will abide by the \htmladdnormallink{CMU Statement of Assurance}{http://www.cmu.edu/policies/documents/SoA.html}.

\subsection{Team}

	Each team shall consist of one driver and five pushers. Each member of a team must be currently enrolled in a degree seeking program, an Activities Fee paying undergraduate or graduate student of Carnegie Mellon University, and must be a member of the organization entering the buggy. In the case of Greek organizations, members are limited to pledges and initiated members of that chapter and must be, or have been, listed on an IFC membership roster or Panhellenic roster in the case of a sorority. The driver for any team may be any eligible student. For Raceday 2023, there are additional guidelines that can be found in \ref*{Greek}. 

	Fraternities may have female push teams. These women do not need to be on the IFC roster of said fraternity. Sororities may have male push teams. These men do not need to be on the Panhellenic roster of said sorority.

	Last semester seniors shall be considered to be full-time students(regardless of credits carried) and must pay the Activities Fee for the semester in which they participate in buggy. Any graduate student may participate in buggy for any organization (Greek or independent) given they are full-time students of Carnegie Mellon University and have paid the applicable Activities Fee for graduate students. All potential team members of any organization must necessarily have been named previously on the general membership roster submitted by the organization.

\subsection{Alternate Team}

	Each entry may have one alternate team consisting of five pushers and one driver. Each member of an alternate team must comply with all the same requirements that an entry's team members must comply with. No person may be a member of more than one team and one alternate team in each class of competition. A member of an entry's alternate team may substitute for any of that entry's team members.

	Any team member who is substituted for may not compete on any other entry's team on the same day unless he or she is also acting as a substitute for a member of a different team that day. If any team member of an organization is substituted for, at least one other team member from that organization must not compete that same day. For example, if a “B” team member substitutes for an “A” team member, a “C” team member may substitute for the “B” team member even though that person is still competing that same day provided that the “A” team member does not compete that day. In this way several substitutions can take place in order to cover an injury to a member of any team, but a member of one team can't switch places with a member of another team.	

\subsection{Membership Roster}

	Each organization must submit a membership roster to the Sweepstakes Chairman or anyone designated by that Chairman. This roster must be submitted at least ten days prior to the date scheduled for the preliminary races. This roster must include the names and AndrewIDs of all members of that organization who may wish to be members of any of that organization's teams or alternate teams in the Sweepstakes competition. A person listed on this roster does not necessarily need to then participate in Sweepstakes Races. This roster cannot be changed after it is submitted.

\subsection{Design Competition}

	Each organization entering the race competition must also participate in the display portion of the Design Competition.

\section{Number of Entries}

\subsection{Men's Races}

	Each participating organization may have a maximum of four entries in the men's races, but no more than one more entry than that organization had during the previous year's races unless they obtain express consent by a majority vote of the Buggy Chairmen and approval of the Sweepstakes officials.

\subsection{Women's Races}

	Each participating organization may have a maximum of four entries in the women's races, but no more than one more entry than that organization had during the previous year's races unless they obtain express consent by a majority vote of the Buggy Chairmen and approval of the Sweepstakes officials.

\subsection{Design Competition}

	Each participating organization must display all of its buggies scheduled to compete in the Sweepstakes races at the display portion of the Design Competition. In addition, each organization may enter a maximum of two buggies in the presentation portion of the Design Competition.

\section{Fees}

	Checks submitted for the payment of fees should be made payable to Carnegie Mellon University. Payments may also be made by a funds transfer from an organization's campus account into the Sweepstakes account. 

\subsection{Race Entry Fees}

	Race entry fees must be paid to the Sweepstakes Advisor, or anyone designated by the Sweepstakes Advisor, at least one day before the day that heats are selected for the preliminary races unless otherwise specified by the Sweepstakes Advisor or the Sweepstakes Chairman. Race entry fees should be paid separately for each class of race competition.

	\begin{itemize}
		\item First Entry (Men's/Women's) \$50.75
		\item Second Entry (Men's/Women's) \$36.25
		\item Third Entry (Men's/Women's) \$21.75
		\item Fourth Entry (Men's/Women's) \$21.75
	\end{itemize}

\subsection{Design Entry Fees}

	There shall be no entry fees for the design competition.


