\chapter{General Safety Requirements and Procedures}

\section{Buggy Safety}

\subsection{Safety Inspection Requirements}

	The requirements for the safety inspection of buggies shall be as follows:
	\newline

	Each buggy must successfully complete a safety inspection each school semester,
	before it shall be permitted to participate in any freeroll practice, push
	practice, or Sweepstakes race during that semester at Carnegie Mellon
	University. The purpose of this safety inspection is to determine if the buggy
	being inspected complies with all of the Buggy Construction and Performance
	Requirements specified by these Rules, Regulations, and Procedures. Each
	buggy's sponsoring organization has the burden of proof to demonstrate that
	that buggy meets or exceeds ALL of these requirements.

	There shall be no limit to the number of times that a buggy may try to
	successfully complete a safety inspection.

	Safety inspections shall be conducted by the Safety Chairman or anyone
	designated by the Sweepstakes Advisor.

	Any buggy that is involved in any accident during a freeroll practice or push
	practice, may be required to again successfully complete a safety inspection,
	if the Sweepstakes Chairman or the Safety Chairman, so requests, before that
	buggy shall be permitted to participate in any future practice sessions at
	Carnegie Mellon University.

	Any buggy that is modified in any way which might affect the safety of that
	buggy after it has successfully completed a safety inspection, must
	successfully complete an additional safety inspection before it shall be
	permitted to participate in any freeroll practice, push practice, or
	Sweepstakes race at Carnegie Mellon University. Any buggy found to be
	participating in any type of practice session or race competition after a
	safety related modification, and before this additional safety inspection,
	shall be penalized by being banned from any further participation in any type
	of practice sessions and by being disqualified from all race competition for
	that entire school year.
	\newline

	\noindent Modifications considered to affect the safety of a buggy include, but are
	not limited to changing any of the following:
	
	\begin{itemize}
		\item Configuration of the braking system.
		\item Driver's personal protection equipment
		\item Helmet
		\item Safety harness attachment method or construction.
		\item Driver's protective cage.
		\item Shell or windscreen.
		\item Configuration of the steering system.
		\item Diameter of any wheel or tire by more than 0.5 inches.
		\item Position of any wheel relative to the frame or the other wheels.
		\item Tire on any wheel from a solid tire to a pneumatic tire or vice versa.
		\item Attachment method for any wheel.
		\item Aerodynamic covering or shroud of any wheel.
		\item Attachment method or transparency of any windscreen.
		\item Any change that could affect the driver's field of vision.
	\end{itemize}

	\noindent Any buggy that varies its configuration while it is on the buggy course, must
	be capable of successfully completing a safety inspection, in any of its
	different configurations. These variations can include, but are not limited to,
	changing the following:

	\begin{itemize}
		\item Wheel position relative to the frame, the other wheels, or the center of mass of the buggy.
		\item Number of wheels in contact with the ground.
		\item Position of the driver relative to the frame of the buggy.
		\item Position of any part of the pushbar relative to the frame of the buggy.
	\end{itemize}

\subsection{Safety Inspection Procedures}

	Each safety inspection shall consist of two parts, the design inspection and
	the performance demonstration.

\subsubsection{Design Inspection}

	The design inspection shall be a demonstration to the inspector that the buggy
	meets or exceeds all of the buggy construction requirements specified by these
	Rules, Regulations, and Procedures.
	\newline

	\noindent Each design inspection shall be conducted as follows:

	\begin{itemize}

		\item
		A representative of the organization desiring to have a buggy design inspected
		shall contact the Safety Chairman and make an appointment for that inspection.

		\item
		At the appointed time and place, the Safety Chairman shall perform a design
		inspection of the organization's buggy. This design inspection shall be
		performed in accordance with the Design Inspection Checklist provided and kept
		by the Safety Chairman. A copy of the Design Inspection Checklist may be
		obtained from the Sweepstakes Advisor through the Safety Chairman.

		\item
		Representatives of each buggy's sponsoring organization shall demonstrate at
		that buggy's design inspection, that the buggy complies with all of the
		construction criteria specified in the Buggy Construction and Performance
		Requirements section of these Rules, Regulations, and Procedures. This
		demonstration can be either theoretical or experimental, i.e. the design
		features of a buggy may be shown by engineering analysis, drawings, and
		calculations, or they may be shown by an actual demonstration of those
		features, such as actually showing the inspector the buggy and its hardware and
		how it operates. In either case the buggy under inspection must be presented to
		the inspector for actual viewing.

		\item
		Successful completion of a prior design inspection by a buggy shall NOT be
		considered as a contributing factor in evaluating a buggy during a design
		inspection. Each buggy MUST comply with all of the CURRENT construction
		requirements in order to successfully complete a design inspection.

		\item
		A driver that fits in each buggy being design inspected shall be present during
		the inspection in order to demonstrate the adequacy of the driver's personal
		protection features of the buggy, and the fit of the driver inside the driver's
		protective cage.

		\item
		The inspector shall permanently record on the Design Inspection Checklist any
		and all information pertinent to the condition of the buggy being inspected.
		The inspector shall also record some identifiable feature or marking that is
		on, or is a part of, a permanent structure of that buggy. This feature or
		marking will be used during any subsequent safety inspections, spot safety
		checks, braking capability tests, or field of vision tests to uniquely identify
		that buggy. This information shall be kept on file by the Sweepstakes Advisor
		for future reference, as long as that particular buggy is active in Sweepstakes
		practice sessions or races. This information shall be used by present and/or
		future Safety Chairmen and design inspectors to evaluate changes made to a
		buggy after its initial design inspection.

	\end{itemize}

\subsubsection{Performance Demonstration}

	The performance demonstration shall be a demonstration to the inspector that
	the buggy can successfully complete the field of vision test, the braking
	capability test, and the drop brake test specified in the Buggy Construction
	and Performance Requirements section of these Rules, Regulations, and
	Procedures. It shall also be an on-going demonstration to the Safety Chairman,
	of the buggy's actual performance during both freeroll and push practices.
	\newline

	\noindent The performance demonstration portion of the safety inspection shall consist of
	the following:

	\begin{itemize}	

		\item
		Successful completion of the braking capability test specified in the Buggy
		Construction and Performance Requirements section of these Rules, Regulations,
		and Procedures. The braking capability test shall be conducted at a time and
		placed arranged by appointment with the Safety Chairman or anyone designated by
		that Chairman.

		\item
		Successful completion of the field of vision test specified in the Buggy
		Construction and Performance Requirements section of these Rules,Regulations,
		and Procedures. The field of vision test can usually be performed at the same
		time and place as the braking capability test.

		\item
		Successful completion, when required, of the drop brake test specified in the
		Buggy Construction and Performance Requirements section of these Rules,
		Regulations, and Procedures. The drop brake test shall be conducted whenever
		required before freeroll practices, after races, or during spot safety checks.
		The Safety Chairman may require an additional design inspection and braking
		capability test if a buggy frequently fails the drop brake test on its first
		attempt of the day.

		\item
		An on-going demonstration that the buggy's steering and control systems can be
		operated in a stable manner. The stability and performance of a buggy's
		steering and control systems and of that buggy's driver shall be observed by
		the Safety Chairman, and/or anyone designated by that Chairman, whenever that
		buggy is participating in any type of practice session at Carnegie Mellon
		University.

		If the Safety Chairman determines that a buggy and/or its driver is not stable,
		that buggy and/or driver shall not be permitted to participate in any
		subsequent freeroll practices or push practices until the cause of that
		instability has been eliminated. The Safety Chairman may require an additional
		design inspection or may ban a buggy from any future practices or races if that
		buggy consistently exhibits erratic control or performance at any practice
		session.

		\item
		An on-going demonstration of the buggy's static and dynamic lateral stability
		during freeroll and push practices (i.e. the buggy must demonstrate by its
		performance during practices that it is laterally stable while it is both at
		rest and in motion, and that it can be used during practice sessions without
		tipping over, rolling over, or having one or more wheels lift off the ground
		while it is cornering).

		The static and dynamic lateral stability of a buggy shall be observed by the
		Safety Chairman, and/or anyone designated by that Chairman, whenever that buggy
		is participating in any type of practice session at Carnegie Mellon University.
		If the Safety Chairman determines that the static or dynamic lateral stability
		of a buggy is not adequate (due to tipping over, rolling over, or having one or
		more wheels lift off the ground when cornering), that buggy shall not be
		permitted to participate in any subsequent freeroll practices or push practices
		until the cause of that instability has been eliminated. The Safety Chairman
		may require an additional design inspection, or may ban a buggy from any future
		practices or races if that buggy continues to exhibit erratic static or dynamic
		lateral stability at any practice session.

	\end{itemize}

\subsection{Spot Safety Checks}

	At any time during any type of buggy practice session at Carnegie Mellon
	University, the Sweepstakes Chairman, Assistant Chairman, Safety Chairman, or
	anyone designated by the Sweepstakes Advisor, may perform a spot safety check
	on any buggy participating in that practice session. A spot safety check shall
	consist of checking any or all of the following:

	\begin{itemize}

		\item Performance of a drop brake test to determine if the buggy's braking
		system is working properly.

		\item Helmet, mouthguard, goggles, windscreen, interior windscreen (where required), 
		harness, and gloves of the buggy driver. Additionally, the manner in which each is 
		secured should be checked to ensure safety and clear visibility without 
		obstructions.

		\item Lights and reflectors, when they are required,
		such as during after dark drop brake tests and push practices.

		\item General condition of the buggy to ensure that it is in as
		good, or better condition, in regards to safety related items, as it was during
		its safety inspection, and that no modifications have been made to the buggy
		since its inspection which could reduce its safety.

	\end{itemize}

	Any buggy found to be out of compliance with any applicable safety rules and
	regulations during a spot safety check shall not be permitted to participate in
	any type of practice session for the remainder of that day and that buggy's
	sponsoring organization shall be fined the amount of \$25.00 for the first
	occurrence and \$50.00 for any additional occurrences by that organization
	during that school year. If a buggy is found to be out of compliance with any
	applicable safety rules and regulations during a spot safety check on more than
	one occasion during any one school year, that buggy shall not be permitted to
	participate in any type of practice session or Sweepstakes race for the
	remainder of that school year.

\section{Driver Safety}

\subsection{Education Program}

	Each buggy driver MUST participate in a driver education program before they
	will be permitted to drive a buggy during any type of buggy practice session at
	Carnegie Mellon University. The driver education program shall consist of the
	following:
	\newline

	Before any freeroll practice takes place during the fall semester of each
	school year, a meeting of all of the people who want to be buggy drivers shall
	be held. This meeting shall be conducted by the Sweepstakes Chairman, the
	Assistant Chairman, the Safety Chairman, and/or anyone designated by the
	Sweepstakes Chairman. Buggy Chairmen from individual organizations shall not be
	permitted to attend the first at least a portion (usually the first hour) of
	this meeting unless they are also buggy drivers.

	Topics that shall be discussed at this meeting shall include, but not be
	limited to, the following:

	\begin{itemize}
		\item A map of the course, detailing the normal path of a buggy from start to finish.
		\item Potential dangers of buggy driving.
		\item Rules, Regulations, and Procedures relative to driving a buggy.
		\item Driver's personal safety and protective equipment.
		\item Driver training methods.
		\item Driving techniques for both normal and emergency situations.
		\item Safety procedures during emergency situations, including instructing the driver to remain in the buggy if possible when they come to any emergency stop.
		\item Use of signal flags, including the required chute flaggers and the yellow colored emergency flag. 
	\end{itemize}

	In addition to the discussions at this meeting, each potential driver shall be
	given a written summary of the topics covered during this meeting.

	Topics that shall be discussed at the spring semester driver's education
	meeting shall include, but not be limited to, all of the same topics covered
	during the fall semester buggy driver's education meeting.

	Approximately one week before the preliminary races are scheduled each school
	year, a meeting of all of the people who are to drive buggies during those
	races shall be held. This meeting shall be conducted by the Sweepstakes
	Chairman, the Assistant Chairman, the Safety Chairman, and/or anyone designated
	by the Sweepstakes Chairman. Buggy Chairmen from individual organizations will
	usually, but not always, be permitted to attend all of this meeting. Topics
	that shall be discussed at this meeting shall include, but not be limited to, a
	review of all of the topics covered during the previous buggy driver's
	education meetings, plus a detailed discussion and review of race day
	procedures and regulations, and driving techniques that can be employed during
	the races.

	Additional driver education meetings may be held at the discretion of the
	Sweepstakes Advisor, the Sweepstakes Chairman, or the Safety Chairman.

	Attendance at ALL of the required driver education meetings is MANDATORY for
	anyone who wants to drive a buggy at Carnegie Mellon University. If a person
	who wants to be a buggy driver fails to attend any of the required meetings, he
	or she must submit a request (either written or verbal) for a review of the
	content of each missed meeting to the Sweepstakes Chairman. This request must
	state the reason that each meeting in question was missed. The Sweepstakes
	Chairman shall then require that person to review the content of each missed
	meeting with someone that he or she designates.

\subsection{Liability Waiver}

	Each potential buggy driver must sign a Waiver of liability form (this is
	usually done at the buggy driver's education meeting). No person shall be
	permitted to drive a buggy at any type of practice session or Sweepstakes race
	at Carnegie Mellon University, until they have signed this form. These waiver
	forms shall be kept on file by the Sweepstakes Advisor. A copy of this waiver
	form can be obtained from the Sweepstakes Advisor through the Safety Chairman.
	If the buggy driver is less than 18 years of age, that driver's parent or legal
	guardian must also sign that waiver form.

\subsection{Pass Test}

	Each buggy driver must successfully complete a pass test during a spring
	semester freeroll practice session in each buggy that he or she will be driving
	during the Sweepstakes races before he or she will be permitted to compete in
	those races. The purpose of this pass test is to demonstrate that each driver
	has certain minimum driving skills while driving the buggy that they will be
	racing in. The procedure for the pass test shall be as follows:
	\newline

	The test shall take place during a freeroll practice session while the driver
	and buggy being tested are freerolling on the buggy course. Arrangements to
	have the test observed by a qualified observer must be made by the organization
	taking the test with the Safety Chairman, or anyone designated by that
	Chairman, prior to the test.
	\newline

	\noindent The test shall be conducted as follows:

	\begin{itemize}

		\item A buggy and driver not taking the test shall be allowed to freeroll
		down the buggy course. If the organization being tested has more than one
		buggy, it must use one of its own buggies as the buggy being passed. If it only
		has one buggy, it may use a buggy from another organization, but that buggy may
		only be a buggy that is already qualified for the races, i.e. that buggy must
		have already been driven down the buggy course at least five times and have
		successfully completed its own pass test.

		\item The buggy and driver taking the test shall be allowed to freeroll
		down the buggy course after the first buggy, at a speed that is greater than
		that of the first buggy, so that the buggy and driver taking the test may
		eventually overtake the first buggy.

		\item The buggy and driver taking the test shall pass the first buggy and
		driver somewhere between the George Westinghouse Memorial Pond and the service
		driveway that extends eastward onto Flagstaff Hill from Frew Street,
		approximately halfway between Schenley Drive and Scaife Hall.

		\item The test shall be observed by the Safety Chairman, or anyone
		designated by that Chairman. This observer shall ride in a follow car
		immediately behind the two buggies participating in the test.

	\end{itemize}

	\noindent To successfully complete the test, the following requirements must be met:

	\begin{itemize}

		\item The test observer must agree that the pass was adequate, based on
		that observer's judgment and experience.

		\item The buggy being passed must be moving at a reasonable speed, as
		determined by the test observer.

		\item The pass must take place somewhere between the George Westinghouse
		Memorial Pond and the service driveway that extends eastward onto Flagstaff
		Hill from Frew Street, approximately halfway between Schenley Drive and Scaife
		Hall.

		\item The pass must demonstrate the skill of the passing driver (i.e. the
		passing buggy must come up behind the slower buggy, smoothly pull out to one
		side of it, pass it, and then smoothly pull over in front of the passed buggy).
		The passing buggy must appear to be in control at all times during the pass and
		must not exhibit any instability attributable to either the driver or the
		buggy. The driver of the passing buggy must leave adequate clearance when
		passing the slower buggy and must return to his or her desired course smoothly
		after the pass has been completed. The manner in which the pass is made must
		demonstrate to the observer that the passing driver is able to adequately judge
		the position of his or her buggy relative to the buggy being passed.

	\end{itemize}

\section{Accidents}

	\noindent A buggy shall be considered to have been involved in an accident when any of the following events occur:

	\begin{itemize}
		\item Departure from the course while freerolling or racing.
		\item Contact with any border of the buggy course, such as a hay-bale or curb.
		\item Contact with any material obstruction, such as another buggy, a person, bicycle, motor vehicle, etc.
		\item Any complete stop that is not due to normal uphill or deliberate human deceleration.
		\item Any part such as the shell, a hatch, a cover, etc., falls	off while freerolling or racing.
	\end{itemize}

	
\subsection{Accident Report}

	Any buggy that is involved in any type of accident during any type of practice
	session at Carnegie Mellon University may not be used in any type of practice
	session again until that buggy's sponsoring organization has submitted an
	accident report to the Safety Chairman, or anyone designated by that Chairman,
	and had that report approved by the Sweepstakes Chairman or the Safety
	Chairman. In any case this report must be submitted within 48 hours of the time
	that the accident occurred. The form to be used for this accident report can be
	obtained from the Sweepstakes Advisor through the Safety Chairman. Accident
	reports will not be approved unless the Sweepstakes Chairman or the Safety
	Chairman consider that the problem that caused the accident has been corrected
	and that a similar accident is not likely to occur again. The Sweepstakes
	Chairman or the Safety Chairman may require any buggy that has been involved in
	an accident to again successfully complete a safety inspection before that
	buggy is permitted to participate in any future practice session.

\subsection{Accident Procedures}
	
	\subsubsection{Medical Personnel Avaliable}
	If an accident does occur and medical personnel are in attendance at that 
	practice session or race, they
	should be dispatched to the scene of that accident as quickly as possible. In
	this case they will have the responsibility of determining the condition of any
	victims and of providing any needed first aid. If no medical personnel are
	immediately available, the responsibility of aiding any accident victims will
	be borne by either the Carnegie Mellon University Campus Police or the City of
	Pittsburgh Police who are in attendance.
	
	In the event of a collision where EMS is present, the members of the
	sponsoring buggy's organization will cooperate fully with the EMS and allow
	the medical staff access to the driver. Generally, EMS personnel will seek
	to communicate briefly with the driver to determine the condition of that
	driver. If any member of that organization hinders, or allows an alumni to
	hinder access to the driver by EMS personnel, that organization may be
	entirely disqualified from that year's races, at the collective discretion
	of the Sweepstakes Chairman, Assistant Sweepstakes Chairman, and Saftey
	chairman.

	\subsubsection{Medical Personnel Unavailable}
	If no medical personnel are immediately available, the Safety Chairman
	and/or Sweepstakes Chairman shall be dispatched to the scene of the collision.
	Once at the scene the Safety Chairman and/or Sweepstakes Chairman will
	determine the proper course of action. After looking for any sign of apparent
	or suspected injury, they will determine if the driver should be removed from
	the buggy and whether medical assistance should be dispatched. Common factors
	in making this determination include but are not limited to: speed at the time
	of collision, disruption of barriers, and witness testimony. 

	Before any assistance arrives at the scene of an accident, common sense should
	be observed. The victim should not be moved or disturbed in any way unless
	there is some other danger in not doing so. If a buggy is involved in an
	accident and comes to rest in a position where it may be impacted by another
	buggy that is freerolling behind it, that buggy should be immediately moved, as
	quickly and as gently as possible, to a position of safety. If a buggy needs to
	be immediately moved from a dangerous position after an accident, ANYONE near
	it may do so, even if they are not members of that buggy's sponsoring
	organization. 

	In the event of a collision the buggy and its driver should not be moved or
	disturbed until available assistance arrives and assesses the situation. In
	general, a buggy driver should not be removed from a buggy until a responsible
	authority advises that it is wise to do so. In ABSOLUTELY NO CASE should an
	unconscious driver be removed from a buggy without the supervision of medical
	personnel, nor should the drivers helmet be removed.
	
	\subsubsection{Buggy Procedures after an Accident}
	Any buggy involved in an accident should not be moved or tampered with in any 
	manner unrelated to rendering medical assistance to the driver. Once the driver 
	is safe, free, and clear of the buggy a blanket may be placed over the buggy for
	protection. However, the buggy may not be removed from the scene or otherwise 
	tampered with until after an appropriate assessment of the buggy can be made. 
	Only once permission is explicitly granted by the Safety Chairman, Chairman, or 
	Advisor may the buggy be removed for any purpose not medically related. 
	Inappropriate removal of the buggy will result in an immediate spot safety 
	failure, at the discretion of the Safety Chairman, Chairman, and Advisor. 
	Any movement and modification necessary to the rendering of medical assistance 
	must be permitted.

	Additionally, organizations and witnesses should cooperate with the Safety
	Chairman's documentation of the collision for Sweepstakes and University
	Records.
	
	\subsubsection{Accident Safety Measures}
	Organizations are encouraged to position people near the chute portion of the
	buggy course during freeroll practices so that someone will be available to
	provide any needed assistance in the event that one of their buggies is
	involved in an accident. 
	
	Organizations are also encouraged to keep blankets
	in their follow cars to keep their drivers warm or cover their buggies when the
	driver is sufficiently warm.